% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 


\begin{document}

\name{Corry Haines}
\address{Foster City, CA 94404}
\address{\sl tabletcorry@gmail.com}

\begin{resume}
 
\section{SKILLS/ EXPERIENCE} {\sl Languages (Skilled):} Python, Bash.\\
                {\sl Languages (Familiar):} Java, C\#, C, Haskell, SQL, Ruby, Javascript.\\
                {\sl Platforms:} Linux (Ubuntu, CentOS, Arch), OS X, Windows. \\
                {\sl Data:} Postgres, MySQL, Memcached, Hadoop. \\
                {\sl Systems:} Collectd, Graphite, Gerrit, Jenkins, Puppet, Nagios, Fabric, Flask, git, svn.
 
\section{FULL-TIME EXPERIENCE} 
                {\sl Ground Control Operations} \hfill September 2010 - Present \\
                Rocket Fuel, Redwood City, CA
                \begin{itemize}  \itemsep -2pt
                 \item Deployed scalable metrics collection and graphing system.
                 \item Migrated development from SVN to git.
                 \item Migrated build system from Ant to Maven.
                 \item Migrated deployment system from bash to Fabric.
                 \item Deployed Gerrit code review for all projects.
                 \item Deployed LDAP system for cohesive authentication.
                 \item Maintained and improved Puppet configuration system.
                 \item Assisted in hardware planning, deployment, and maintenance.
                 \item Assisted in network setup and maintenance.
                 \item Assisted in MySQL maintenance and scaling.
                \end{itemize}

                {\sl Quality Assurance \& Operations Engineer} \hfill June 2009 - September 2010 \\
                Truviso, Foster City, CA
                \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed benchmarking tools to compare competitors' products against own.
                 \item Developed several automated test suites for database product.
                 \item Migrated issue tracking from Trac to Jira.
                 \item Maintained and improved existing Truviso development servers.
                 \item Planned cloud infrastructure for ambitious project.
                 \item Built data processing system on Cassandra/Memcached and Python.
                \end{itemize}
                
\section{EDUCATION} {\sl Bachelor of Science,} Computer Science \hfill    2005 - 2009 \\
                Rochester Institute of Technology, Rochester, NY
                
\section{INTERNSHIP EXPERIENCE}
                
                {\sl Software Development Intern} \hfill        Summer 2008 \\
                Laszlo Systems, San Mateo, CA
                
                {\sl Night Systems Operator} \hfill        Winter-Spring 2008 \\
                Rochester Institute of Technology, Rochester, NY
                
                {\sl Software Development Intern} \hfill        Summer 2007 \\
                Citrix Systems, Fort Lauderdale, FL
                
                {\sl Assistant System Administrator} \hfill        Winter-Spring 2007 \\
                Rochester Institute of Technology,  Rochester, NY
                
                {\sl Software Development Intern} \hfill          Summer 2006 \\
                Microsoft, Redmond, WA
           
\section{Achievements}             
            Eagle Scout, Boy Scouts of America (2005) \\
 
\end{resume}
\end{document}







